A weighted sampling algorithm to designing RNA sequences with target secondary structure and nucleotide distribution

### 2013-01-08 ISMB/supplementary_ISMB.tex
last

%!TEX root = main_ISMB.tex
\section{Supplementary data}
\subsection{Benchmark \ourprog vs \RNAinverse}
Using the same dataset of $50$ structures, we generated $100$ samples
per structure with \RNAinverse. They yield for most parameters
a high entropy.
Table.~\ref{tab:nb_rnainv} contains the number of sample with a given \GCContent generated by \RNAinverse. The vast majority resides around $50\%-70\%$, showing one of its major deficiencies. 
 For all structures that have been solved 
by the three methods, only \RNAinverse, only \texttt{Incarnation} and
\texttt{Incarnation} followed by \RNAinverse, 
we present for every different concentration of \GCContent
the average sample entropy and the average base pairs entropy in Figure.~\ref{fig:rnainverse}.

@@

\begin{figure}[ht!]
	%\centering
	\hspace{-5em}
	\includegraphics[scale=0.4]{Figures/RNAinverse_data_100.png}
	\caption{Entropy and \GCContent  for structures solved by
	the 3 methods.}
	\label{fig:rnainverse}
\end{figure}

>>>>

%!TEX root = main_ISMB.tex
\section{Supplementary data}
\subsection{Benchmark \ourprog vs \RNAinverse}
Using the same dataset of $50$ structures, we generated $100$ samples
per structure with \RNAinverse. They yield for most parameters
a high entropy.
Table.~\ref{tab:nb_rnainv} contains the number of sample with a given \GCContent generated by \RNAinverse. The vast majority resides around $50\%-70\%$, showing one of its major deficiencies. 
 For all structures that have been solved 
by the three methods, only \RNAinverse, only \texttt{Incarnation} and
\texttt{Incarnation} followed by \RNAinverse, 
we present for every different concentration of \GCContent
the average sample entropy. and the average base pairs entropy in Figure.~\ref{fig:rnainverse}.

@@

\begin{figure}[ht!]
	\centering
	%\hspace{-5em}
	\includegraphics[scale=0.4]{Figures/RNAinverse_data_100.png}
	\caption{Entropy and \GCContent  for structures solved by
	the 3 methods.}
	\label{fig:rnainverse}
\end{figure}
